SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/motivation.tex
remove todo
Martins final comments

While a failure to be developer friendly may be one reason why the
Semantic Web has not succeeded on a grand scale, my training in
natural science lead me to ask if there may be other reasons that we
do not see the remarkable rate of progress of the natural sciences in
this field. These questions are as hard to ask and to live with as to
answer. \todo{Too fluffy?}

I became early quite confident that the practice of benchmarking was
an easy target, with its lack of summary statistics and inability to
support proper hypothesis testing, standardising to deal with
complexity rather than methodological advances, and lacking in ability to
formulate the experiment as severe enough.

>>>>

While a failure to be developer friendly may be one reason why the
Semantic Web has not succeeded on a grand scale, my training in
natural science lead me to ask if there may be other reasons that we
do not see the remarkable rate of progress of the natural sciences in
this field. These questions are as hard to ask and to live with as to
answer.

I became quite confident at an early stage that the practice of benchmarking was
an easy target, with its lack of summary statistics and inability to
support proper hypothesis testing, standardising to deal with
complexity rather than methodological advances, and lacking in ability to
formulate the experiment as severe enough.
